\boldmath Heavy resonances at energy frontier colliders

### 2019-02-03 paper.tex
Updates from ShareLaTeX

\newcommand{\Zp}{\ensuremath{Z^{\prime}}}
\newcommand{\ZpSSM}{\ensuremath{Z^{\prime}_{\mathrm{SSM}}}}
\newcommand{\Z}{\ensuremath{Z}}
\newcommand*{\Zptata}{\ensuremath{Z^{\prime}\rightarrow \tau\tau}}
\newcommand*{\Zpee}{\ensuremath{Z^{\prime}\rightarrow \text{ee}}}
\newcommand*{\Zpmumu}{\ensuremath{Z^{\prime}\rightarrow \mu\mu}}
\newcommand*{\Zpll}{\ensuremath{Z^{\prime}\rightarrow \ell\ell}}
\newcommand*{\Zptt}{\ensuremath{Z^{\prime} \rightarrow \ttbar}}
\newcommand{\ptSub}[1]{\ensuremath{p_{\text{T} #1}}}
\newcommand{\ptSup}[1]{\ensuremath{p_{\text{T}}^{#1}}}
\newcommand{\pt}{\ensuremath{p_{\text{T}}}}
\newcommand{\ptEl}{\ensuremath{p_{\text{T}}^{e}}}
\newcommand{\ptMu}{\ensuremath{p_{\text{T}}^{\mu{}}}}
\newcommand{\ptZp}{\ensuremath{p_{\text{T}}^{\ensuremath{Z^{\prime}}}}}
\newcommand{\mZp}{\ensuremath{M_{\ensuremath{Z^{\prime}}}}}
\newcommand{\mSD}{\ensuremath{m_{\ensuremath{SD}}}}
\newcommand{\mll}{\ensuremath{M_{\ensuremath{ll}}}}
\newcommand*{\hht}{\ensuremath{H_{\ensuremath{T}}}}
\newcommand*{\met}{\ensuremath{E_{T}^{\rm{miss}}}}
\newcommand*{\intlumifcc}{\ensuremath{\mathcal{L}=30\,\text{ab}^{-1}}}
\newcommand*{\intlumihelhc}{\ensuremath{\mathcal{L}=15\,\text{ab}^{-1}}}
\newcommand*{\qjj}{\ensuremath{Q^{*} \rightarrow jj}}
\newcommand*{\rsg}{\ensuremath{G_{RS} \rightarrow W^+W^-}}
\newcommand*{\vj}{\ensuremath{\text{V + jets}}}
\newcommand*{\metvec}{\vec{\pt}^{\textrm{miss}}}

@@

\newcommand*{\sqrtslhc}{\ensuremath{\sqrt{s}=\text{14 TeV}}}
\newcommand*{\sqrtshelhc}{\ensuremath{\sqrt{s}=\text{27 TeV}}}
\newcommand*{\sqrtsfcc}{\ensuremath{\sqrt{s}=\text{100 TeV}}}
\renewcommand*{\intlumihelhc}{\ensuremath{\mathcal{L}=15\text{ ab}^{-1}}}
\newcommand*{\intlumihllhc}{\ensuremath{\mathcal{L}=3\text{ ab}^{-1}}}

@@

New machines are built to make direct discoveries, and even though we do not have any guaranted discoveries, we need to make sure that we will cover a large fraction of Beyond the SM (BSM) phase space. Qualitatively, the mass reach should roughly scale by a factor of $\sqrt{s}/14$, so $\sim 7$ for $\sqrt{s}=100$. However, with the parton luminosities evolving with $Q^2$, thus dropping a bit faster at high energy, one typically finds it is only a factor of $\sim 5$ increase. But the statistics are also enhanced by several orders of magnitude for many BSM phenomena, that the LHC could barely touch during its exploitation. It is not only that the mass reach increases by a large factor, but it is the fact that if the LHC were to see some hints of possible new physics, by increasing the energy by a factor seven, we would increase the statistics by two or even three orders of magnitude, and we can use this new machine to study with great accuracy what it is that has been found. In addition we could have the ability to provide firm answers to questions such as: is the SM dynamics all there at the TeV scale, is there a TeV scale solution to the hierarchy problem, is dark matter a thermal wimp (either we discover it as a WIMP, or we discover DM is not a WIMP and it has to be something else), was the cosmological EW phase transition 1st order, etc...

Concerning the topic of this paper, the discovery potential for new resonances not predicted by the SM makes Future Circular Colliders (FCC) the only place to search for such heavy particles, compared to the current LHC and the coming HL-LHC.
In the framework of FCC it is also extremely relevant to discuss the main limitations of the detector in identifying high energetic top-quarks or W/Z bosons. Indeed 100\,TeV proton-proton collisions will produce very large quantities of multi-TeV's bosons or top, thus the design of the detector needs detailed optimisations in order to achieve the required physics goals. The capabilities of such a detector should include the capabilities of measuring multi-TeV leptons, top-quarks and bosons, and will be discussed in this paper.

@@

A new, neutral, spin-1 gauge boson, $\Zp$, which is usually a color-singlet object produced in the $q\bar q$ channel, is a ubiquitous feature of many models that predict new
physics~\cite{Langacker:2008yv,Rizzo:2006nw,Carena:2004xs,Salvioni:2009mt}.  While falling into several distinct classes, $\Zp$ are most commonly associated with the
extension of the the SM electroweak gauge group by an additional U(1) or SU(2) factor although more significant augmentations are possible. When the additional factor is non-abelian,
as in the case of SU(2), a new $W^\pm$' gauge boson generally also appears in the spectrum together with the $\Zp$ and with a comparable mass.  Of this subset of models, those
that arise from Grand Unified Theory frameworks are the ones most commonly encountered in the literature and include familiar examples such as the Left-Right Symmetric
Model (LRM)~\cite{Senjanovic:1975rk,Senjanovic:1975rk,Mohapatra:1980yp} which results from SO(10)
(or larger GUT groups) and where the SM is augmented by an SU(2)$_R$ factor. Most simply, the LRM can arise, e.g., from SO(10) GUT breaking directly to
SU(2)$_L \times$SU(2)$_R \times$U(1)$_{B-L}$ which then breaks to the SM at the few to multi-TeV scale. A second set of GUT-based $\Zp$ models arise from
$E_6$~\cite{Robinett:1982tq,London:1986dk,Hewett:1988xc,Joglekar:2016yap} where most simply $E_6 \rightarrow$ SM$\times$U(1)$_\psi \times$U(1)$_\chi \rightarrow $ SM$
\times$U(1)$_\theta$, where a new U(1)$_\theta$ gauge group factor is predicted. Note here $\theta$ labels the remaining linear combination of U(1)$_\psi$-U(1)$_\chi$ that remains
unbroken to lower energies (in comparison to the GUT scale).  A common set of features of this GUT-based model class include their possesing generation-universal couplings
of the $\Zp$ to the SM fermions, their charges commuting with those of the SM so that, e.g., $u_L$ and $d_L$ have the same $\Zp$ coupling and the resonances themselves are usually
narrow, reflecting electroweak strength or weaker couplings with width to mass ratios $\Gamma/M < 0.01-0.03$. In particular, the GUT origin of these models
implies that this class of $\Zp$ can be used to simultaneously study all of the dileptonic channels: $e^+e^-,~\mu^+\mu^+$ as well as $\tau^+\tau^-$ together with the dijets and boosted
$t\bar t$ channels as well.

@@

Monte Carlo~(MC) simulated event samples are used to simulate the response of the detector to signal and backgrounds. Signals are generated with \py~\cite{Sjostrand:2014zea} version v8.201 with the \pdf{NNPDF2\!.\!3NNLO} PDF set~\cite{Ball:2014uwa} using the leading order cross-section from the generator with no k-factor. The SM backgrounds are Drell-Yan, di-jet (QCD), top pairs (\ttbar), $VV$ and \vj\ where $V=W/Z$,  were generated using \MGAMC~\cite{Alwall:2014hca} v2.5.5 at leading order only with the \pdf{NNPDF3\!.\!0NLO}~\cite{Ball:2014uwa} PDF set in bins of $\hht$. A k-factor of 2 is applied to all the background processes to account for higher order corrections.

@@

This study discusses the discovery potential of heavy resonances decaying to multi-TeV final states. The ability to accurately reconstruct highly boosted final states is largely dependent on the nature of the object and on the detector assumptions. Generally speaking, the energy-momentum resolution of calorimetric objects such as electrons, photons and jets improves as a function of the energy. Conversely, the momentum resolution of charged particles reconstructed as tracks decrease with the momentum as the curvature of the trajectory vanishes. In addition, at high energies, composite objects such as jets, or hadronically decaying tau's and heavy bosons tend to be highly collimated. This results in an effectively coarser granularity of the detector, which can potentially limit the ability to resolve and identify the decay products inside the jets, thereby limiting the identification and QCD background rejection capabilities.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.56\columnwidth]{Fig/dtf.pdf}
  \includegraphics[width=0.42\columnwidth]{Fig/jetalgo.pdf}
  \caption{Left: Track reconstruction efficiency inside highly QCD boosted jets as function of the angular distance $\Delta R$ between the track and the center of the jet for different assumptions on the tracker spatial resolution. Right: Reconstructed 
  "soft-dropped" jet mass of highly boosted top and QCD jets with various sets of input to the jet clustering algorithm: tracks only, calorimeters towers only and particle-flow candidates. }
  \label{fig:substructure}
\end{figure}

@@

\begin {table}
\begin{center}
\begin{tabular}{l||c|c}
& HE-LHC & FCC-hh \\
  \hline
  \hline
$B_z$ $(T)$ &  4 & 4 \\
  \hline
Length $(m)$ & 6 & 10 \\
 \hline
Radius $(m)$ & 1.1 &  1.5 \\
 \hline
$\epsilon$ & 0.95 & 0.95\\
\hline
$\sigma(\eta,\phi)$ & 3 mrad & 1 mrad \\
\hline
$\sigma(p_T)/p_T$ (tracks) &  $0.1\cdot \pt$ (TeV/c) &  $0.02\cdot \pt$ (TeV/c)\\
\hline
$\sigma(p_T)/p_T=5\%$ (muons) & $\pt=2$~TeV & $\pt=15$~TeV\\

@@

\begin {table}
\begin{center}
\begin{tabular}{l||c|c}
& HE-LHC & FCC-hh \\
  \hline
  \hline
$\sigma(E)/E $ (ECAL)& 10\%/$\sqrt{E} \oplus 1\%$ &  10\%/$\sqrt{E} \oplus 1\%$\\
   \hline
$\sigma(E)/E $ (HCAL)& 50\%/$\sqrt{E} \oplus 3\%$  &  50\%/$\sqrt{E} \oplus 3\%$\\
  \hline
  \hline
$\eta \times \phi$ cell size (ECAL)& $(0.02\times0.02)$ &  $(0.01\times0.01)$\\
  \hline
 $\eta \times \phi$ cell size  (HCAL)& $(0.1\times0.1)$ & $(0.025\times0.025)$
\end{tabular}
\caption{Calorimeter parameters for the HELHC and FCC detectors in Delphes.}
\label{tab:cal_param}
\end{center}
\end{table}
%\caption{Comparison of basic detector performances for FCC-hh and HE-LHC.}

@@

\begin {table}[h]
\begin{center}
\begin{tabular}{ l | c | c | c | c | c }
  & electrons & muons & photons & b-jets & $\tau$-jets\\
  \hline
  \hline
HE-LHC & 95\% & 95\% & 95\% & (1 - \pt~[TeV]/5)$\cdot$75\% & (1 - \pt~[TeV]/5)$\cdot$60\%  \\
FCC-hh & 99\% & 95\% & 95\%  & (1 - \pt~[TeV]/15)$\cdot$85\% & (1 - \pt~[TeV]/30)$\cdot$60\% \\
\end{tabular}
\caption{Global reconstruction efficiency of high \pt\ central objects for the HELHC and FCC detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

@@

\begin {table}[h]
\begin{center}
\begin{tabular}{ l | c | c | c }
  & light (b-tag) & charm (b-tag) & QCD ($\tau$-tag)\\
  \hline
  \hline
HE-LHC & (1 - \pt~[TeV]/5)$\cdot$1\%  & (1 - \pt~[TeV]/5)$\cdot$10\% & (1 - \pt~[TeV]/5)$\cdot$1\%  \\
FCC-hh & (1 - \pt~[TeV]/15)$\cdot$1\% & (1 - \pt~[TeV]/15)$\cdot$5\% & (8/9 - \pt~[TeV]/30)$\cdot$1\% \\
\end{tabular}
\caption{Mis-identification efficiency of high \pt\ central heavy flavour jets for the HE-LHC and FCC detectors in Delphes.}
\label{tab:mistag}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Treatment of the Monte-Carlo samples}
\label{subsec:mctreat}
%\subsection{Tag Rate Function}
%\label{subsec:trf}
The modelling of the backgrounds in the high tagging regimes is a challenging task. The requirement of $b$ tagging in some MC samples can drastically reduce the available statistics.
This shortage of events that pass the $b$-tagging cut in the signal regime, in conjunction with the large cross section of some of the backgrounds can lead to very spiky templates.
To overcome this problem the tag rate function (TRF) method is used. By using the TRF method, no event is cut based on its $b$-tagging count, but instead all the events are weighted.
This weight can be interpreted as the probability of the given event to contain the desired number of $b$ jets.
To achieve this, the tagging efficiency (a function of $\eta$, $\pt$ and true jet flavour) was
used to calculate the event weight based on the kinematics and flavour of the jets found in each event. More details on the method can be found in Appendix~\ref{sec:app:trf}.
Despite the fact that very large amount of Monte-Carlo statistic has been simulated in bins of $\hht$
and the usage of TRF to save events, there are still large statistical fluctuations from high weight events.
In order to reduce this effect, and when large fluctuations are observed, the background spectrum is fitted. Further details on the procedure are given in Appendix~\ref{sec:app:bgfit}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical analysis}
Hypothesis testing is performed using a modified frequentist method based on a profile likelihood that takes into account the systematic uncertainties as nuisance parameters that are fitted to the expected Monte-Carlo. The full shape information is used, which help from the sidebands to reduce the effect of systematics uncertainties in the signal region. The test statistic $q_\mu$ is defined as the profile log-likelihood ratio: $q_\mu = -2\ln({\cal L}(\mu,\hat{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$, where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that maximise the likelihood function (with the constraint $0\leq \hat{\mu} \leq \mu$), and $\hat{\hat{\theta}}_\mu$ are the values of the nuisance parameters that maximise the likelihood function for a given value of $\mu$. In the absence of any significant deviation from the background expectation, $q_\mu$ is used in the CL$_\text{s}$ method~\cite{Junk:1999kv,Read:2002hq} to set an upper limit on the signal production cross-section times branching ratio at the 95\% CL. For a given signal scenario, values of the production cross-section (parameterised by $\mu$) yielding CL$_\text{s} < 0.05$, where CL$_\text{s}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at 95\% CL. For a $5\sigma$ discovery, the quantity 1-CL$_\text{b}$ must be smaller than $2.87 \cdot 10^{-7}$~\cite{Junk:1999kv} and is again computed using the asymptotic approximation.

@@

Events are required to contain two isolated opposite sign leptons with $\pt > 1$\,TeV, $|\eta|$<4 and an invariant mass $\mll > 2.5$\,TeV.
Figure~\ref{figure:leptonicresonances:ll} (top) shows the invariant mass for a 30\,TeV \ZpSSM\ signal for the $ee$ (left) and $\mu\mu$ (right) channels. The mass resolution is better for the $ee$ channel, as expected from calorimeter constant term that dominates the resolution at high \pt.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_ee.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_mm.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_ll_fcc_v02_allxs.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/DiscoveryPotential_ll_comb_rootStyle.eps}
  \caption{Top: Invariant mass for a 30\,TeV signal after full event selection for $ee$ channel (left) and $\mu\mu$ channel (right).
  Bottom: Limit versus mass for the combined di-lepton ($ee$, $\mu\mu$) channel (left) and luminosity for a $5\sigma$ discovery (right) comparing ee, $\mu\mu$ and combined channels.}
  \label{figure:leptonicresonances:ll}
\end{figure}

>>>>

\newcommand{\Zp}{\ensuremath{Z^{\prime}}}
\newcommand{\ZpSSM}{\ensuremath{Z^{\prime}_{\mathrm{SSM}}}}
\newcommand{\ZpTC}{\ensuremath{Z^{\prime}_{\mathrm{TC2}}}}
\newcommand{\Z}{\ensuremath{Z}}
\newcommand*{\Zptata}{\ensuremath{Z^{\prime}\rightarrow \tau\tau}}
\newcommand*{\Zpee}{\ensuremath{Z^{\prime}\rightarrow \text{ee}}}
\newcommand*{\Zpmumu}{\ensuremath{Z^{\prime}\rightarrow \mu\mu}}
\newcommand*{\Zpll}{\ensuremath{Z^{\prime}\rightarrow \ell\ell}}
\newcommand*{\Zptt}{\ensuremath{Z^{\prime} \rightarrow \ttbar}}
\newcommand{\ptSub}[1]{\ensuremath{p_{\text{T} #1}}}
\newcommand{\ptSup}[1]{\ensuremath{p_{\text{T}}^{#1}}}
\newcommand{\pt}{\ensuremath{p_{\text{T}}}}
\newcommand{\ptEl}{\ensuremath{p_{\text{T}}^{e}}}
\newcommand{\ptMu}{\ensuremath{p_{\text{T}}^{\mu{}}}}
\newcommand{\ptZp}{\ensuremath{p_{\text{T}}^{\ensuremath{Z^{\prime}}}}}
\newcommand{\mZp}{\ensuremath{M_{\ensuremath{Z^{\prime}}}}}
\newcommand{\mSD}{\ensuremath{m_{\ensuremath{SD}}}}
\newcommand{\mll}{\ensuremath{m_{\ensuremath{ll}}}}
\newcommand*{\hht}{\ensuremath{H_{\ensuremath{T}}}}
\newcommand*{\met}{\ensuremath{E_{T}^{\rm{miss}}}}
\newcommand*{\intlumifcc}{\ensuremath{\mathcal{L}=30\,\text{ab}^{-1}}}
\newcommand*{\intlumihelhc}{\ensuremath{\mathcal{L}=15\,\text{ab}^{-1}}}
\newcommand*{\qjj}{\ensuremath{Q^{*} \rightarrow jj}}
\newcommand*{\rsg}{\ensuremath{G_{RS} \rightarrow W^+W^-}}
\newcommand*{\vj}{\ensuremath{\text{V + jets}}}
\newcommand*{\metvec}{\vec{\pt}^{\textrm{miss}}}

@@

\newcommand*{\sqrtslhc}{\ensuremath{\sqrt{s}=14\,\text{TeV}}}
\newcommand*{\sqrtshelhc}{\ensuremath{\sqrt{s}=27\,\text{TeV}}}
\newcommand*{\sqrtsfcc}{\ensuremath{\sqrt{s}=100\,\text{TeV}}}
\renewcommand*{\intlumihelhc}{\ensuremath{\mathcal{L}=15\text{ ab}^{-1}}}
\newcommand*{\intlumihllhc}{\ensuremath{\mathcal{L}=3\text{ ab}^{-1}}}

@@

New machines are built to make direct discoveries, and even though we do not have any guaranted discoveries, we need to make sure that we will cover a large fraction of Beyond the SM (BSM) phase space. Qualitatively, the mass reach should roughly scale by a factor of $\sqrt{s}/14$, so $\sim 7$ for FCC at \sqrtsfcc\ and $\sim 2$ for HE-LHC at \sqrtshelhc. However, with the parton luminosities evolving with $Q^2$, thus dropping a bit faster at high energy, one typically finds it is only a factor of $\sim 5$ increase. But the statistics are also enhanced by several orders of magnitude for many Beyond Standard Model (BSM) phenomena, that the LHC could barely touch during its exploitation. It is not only that the mass reach increases by a large factor, but it is the fact that if the LHC were to see some hints of possible new physics, by increasing the energy by a factor seven, we would increase the statistics by two or even three orders of magnitude, and we can use this new machine to study with great accuracy what it is that has been found. In addition we could have the ability to provide firm answers to questions such as: is the SM dynamics all there at the TeV scale, is there a TeV scale solution to the hierarchy problem, is dark matter a thermal wimp (either we discover it as a WIMP, or we find out DM is not a WIMP and it has to be something else), was the cosmological EW phase transition $1^{\mathrm{st}}$ order, etc...

Concerning the topic of this paper, the discovery potential for new resonances not predicted by the SM makes Future Circular Colliders (FCC) the only place to search directly for such heavy particles, compared to the current LHC and the coming HL-LHC.
In the framework of FCC it is also extremely relevant to discuss the main limitations of the detector in identifying high energetic top-quarks or W/Z bosons. Indeed 100\,TeV proton-proton collisions will produce very large quantities of multi-TeV's bosons or top, thus the design of the detector needs detailed optimisations in order to achieve the required physics goals. The capabilities of such a detector should include the capabilities of measuring multi-TeV leptons, top-quarks and bosons, and will be discussed in this paper.

@@

A new, neutral, spin-1 gauge boson, $\Zp$, which is usually a color-singlet object produced in the $q\bar q$ channel, is a ubiquitous feature of many models that predict new
physics~\cite{Langacker:2008yv,Rizzo:2006nw,Carena:2004xs,Salvioni:2009mt}.  While falling into several distinct classes, $\Zp$ are most commonly associated with the
extension of the the SM electroweak gauge group by an additional U(1) or SU(2) factor although more significant augmentations are possible. When the additional factor is non-abelian,
as in the case of SU(2), a new $W^\pm$' gauge boson generally also appears in the spectrum together with the $\Zp$ and with a comparable mass.  Of this subset of models, those
that arise from Grand Unified Theory frameworks are the ones most commonly encountered in the literature and include familiar examples such as the Left-Right Symmetric
Model (LRM)~\cite{Senjanovic:1975rk,Mohapatra:1980yp} which results from SO(10)
(or larger GUT groups) and where the SM is augmented by an SU(2)$_R$ factor. Most simply, the LRM can arise, e.g., from SO(10) GUT breaking directly to
SU(2)$_L \times$SU(2)$_R \times$U(1)$_{B-L}$ which then breaks to the SM at the few to multi-TeV scale. A second set of GUT-based $\Zp$ models arise from
$E_6$~\cite{Robinett:1982tq,London:1986dk,Hewett:1988xc,Joglekar:2016yap} where most simply $E_6 \rightarrow$ SM$\times$U(1)$_\psi \times$U(1)$_\chi \rightarrow $ SM$
\times$U(1)$_\theta$, where a new U(1)$_\theta$ gauge group factor is predicted. Note here $\theta$ labels the remaining linear combination of U(1)$_\psi$-U(1)$_\chi$ that remains
unbroken to lower energies (in comparison to the GUT scale).  A common set of features of this GUT-based model class include their possesing generation-universal couplings
of the $\Zp$ to the SM fermions, their charges commuting with those of the SM so that, e.g., $u_L$ and $d_L$ have the same $\Zp$ coupling and the resonances themselves are usually
narrow, reflecting electroweak strength or weaker couplings with width to mass ratios $\Gamma/M < 0.01-0.03$. In particular, the GUT origin of these models
implies that this class of $\Zp$ can be used to simultaneously study all of the dileptonic channels: $e^+e^-,~\mu^+\mu^+$ as well as $\tau^+\tau^-$ together with the dijets and boosted
$t\bar t$ channels as well.

@@

Monte Carlo~(MC) simulated event samples are used to simulate the response of the detector to signal and backgrounds. Signals are generated with \py~\cite{Sjostrand:2014zea} version v8.201 with the \pdf{NNPDF2\!.\!3NNLO} PDF set~\cite{Ball:2014uwa} using the leading order cross-section from the generator with no k-factor. The SM backgrounds are Drell-Yan, di-jet (QCD), top pairs (\ttbar), $VV$ and \vj\ where $V=W/Z$,  were generated using \MGAMC~\cite{Alwall:2014hca} v2.5.5 at leading order only with the \pdf{NNPDF3\!.\!0NLO}~\cite{Ball:2014uwa} PDF set in bins of $\hht$. A k-factor of 2 is applied to all the background processes to account for higher order corrections and is considered to be very conservative.

@@

This study discusses the discovery potential of heavy resonances decaying to multi-TeV final states. The ability to accurately reconstruct highly boosted final states is largely dependent on the nature of the object and on the detector assumptions. Generally speaking, the energy-momentum resolution of calorimetric objects such as electrons, photons and jets improves as a function of the energy. Conversely, the momentum resolution of charged particles reconstructed as tracks decrease with the momentum as the curvature of the trajectory vanishes. In addition, at high energies, composite objects such as jets, or hadronically decaying $\tau$'s and heavy bosons tend to be highly collimated. This results in an effectively coarser granularity of the detector, which can potentially limit the ability to resolve and identify the decay products inside the jets, thereby limiting the identification and QCD background rejection capabilities.

@@

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.56\columnwidth]{Fig/dtf.pdf}
  \includegraphics[width=0.42\columnwidth]{Fig/jetalgo.pdf}
  \caption{Left: Track reconstruction efficiency inside highly QCD boosted jets as function of the angular distance $\Delta R$ between the track and the center of the jet for different assumptions on the tracker spatial resolution. Right: Reconstructed 
  "soft-dropped" jet mass of highly boosted top and QCD jets with various sets of input to the jet clustering algorithm: tracks only, calorimeters towers only and particle-flow candidates. }
  \label{fig:substructure}
\end{figure}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{l||c|c}
& HE-LHC & FCC-hh \\
  \hline
  \hline
$B_z$ $(T)$ &  4 & 4 \\
  \hline
Length $(m)$ & 6 & 10 \\
 \hline
Radius $(m)$ & 1.1 &  1.5 \\
 \hline
$\epsilon$ & 0.95 & 0.95\\
\hline
$\sigma(\eta,\phi)$ & 3 mrad & 1 mrad \\
\hline
$\sigma(p_T)/p_T$ (tracks) &  $0.1\cdot \pt$ (TeV/c) &  $0.02\cdot \pt$ (TeV/c)\\
\hline
$\sigma(p_T)/p_T=5\%$ (muons) & $\pt=2$~TeV & $\pt=15$~TeV\\

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{l||c|c}
& HE-LHC & FCC-hh \\
  \hline
  \hline
$\sigma(E)/E $ (ECAL)& 10\%/$\sqrt{E} \oplus 1\%$ &  10\%/$\sqrt{E} \oplus 1\%$\\
   \hline
$\sigma(E)/E $ (HCAL)& 50\%/$\sqrt{E} \oplus 3\%$  &  50\%/$\sqrt{E} \oplus 3\%$\\
  \hline
  \hline
$\eta \times \phi$ cell size (ECAL)& $(0.02\times0.02)$ &  $(0.01\times0.01)$\\
  \hline
 $\eta \times \phi$ cell size  (HCAL)& $(0.1\times0.1)$ & $(0.025\times0.025)$
\end{tabular}
\caption{Calorimeter parameters for the HELHC and FCC detectors in Delphes.}
\label{tab:cal_param}
\end{center}
\end{table}
%\caption{Comparison of basic detector performances for FCC-hh and HE-LHC.}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{ l | c | c | c | c | c }
  & electrons & muons & photons & b-jets & $\tau$-jets\\
  \hline
  \hline
HE-LHC & 95\% & 95\% & 95\% & (1 - \pt~[TeV]/5)$\cdot$75\% & (1 - \pt~[TeV]/5)$\cdot$60\%  \\
FCC-hh & 99\% & 95\% & 95\%  & (1 - \pt~[TeV]/15)$\cdot$85\% & (1 - \pt~[TeV]/30)$\cdot$60\% \\
\end{tabular}
\caption{Global reconstruction efficiency of high \pt\ central objects for the HELHC and FCC detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{ l | c | c | c }
  & light (b-tag) & charm (b-tag) & QCD ($\tau$-tag)\\
  \hline
  \hline
HE-LHC & (1 - \pt~[TeV]/5)$\cdot$1\%  & (1 - \pt~[TeV]/5)$\cdot$10\% & (1 - \pt~[TeV]/5)$\cdot$1\%  \\
FCC-hh & (1 - \pt~[TeV]/15)$\cdot$1\% & (1 - \pt~[TeV]/15)$\cdot$5\% & (8/9 - \pt~[TeV]/30)$\cdot$1\% \\
\end{tabular}
\caption{Mis-identification efficiency of high \pt\ central heavy flavour jets for the HE-LHC and FCC detectors in Delphes.}
\label{tab:mistag}
\end{center}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Treatment of the Monte-Carlo samples}
\label{subsec:mctreat}
The modelling of the backgrounds in the high tagging regimes is a challenging task. The requirement of $b$ tagging in some MC samples can drastically reduce the available statistics. This shortage of events that pass the $b$-tagging cut in the signal regime, in conjunction with the large cross section of some of the backgrounds can lead to very spiky templates. To overcome this problem the tag rate function (TRF) method is used. By using the TRF method, no event is cut based on its $b$-tagging count, but instead all the events are weighted. This weight can be interpreted as the probability of the given event to contain the desired number of $b$ jets. To achieve this, the tagging efficiency (a function of $\eta$, $\pt$ and true jet flavour) was used to calculate the event weight based on the kinematics and flavour of the jets found in each event. 
Despite the fact that very large amount of Monte-Carlo statistic has been simulated in bins of $\hht$ and the usage of TRF to save events, there are still large statistical fluctuations from high weight events. In order to reduce this effect, and when large fluctuations are observed, the background spectrum is fitted. Further details on the TRF and fitting procedure are given in Appendix~\ref{sec:app:trf}.
and~\ref{sec:app:bgfit} respectively.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Statistical analysis}
Hypothesis testing is performed using a modified frequentist method based on a profile likelihood that takes into account the systematic uncertainties as nuisance parameters that are fitted to the expected Monte-Carlo. The full shape information is used, which help from the sidebands to reduce the effect of systematics uncertainties in the signal region. The test statistic $q_\mu$ is defined as the profile log-likelihood ratio: $q_\mu = -2\ln({\cal L}(\mu,\hat{\hat{\theta}}_\mu)/{\cal L}(\hat{\mu},\hat{\theta}))$, where $\hat{\mu}$ and $\hat{\theta}$ are the values of the parameters that maximise the likelihood function (with the constraint $0\leq \hat{\mu} \leq \mu$), and $\hat{\hat{\theta}}_\mu$ are the values of the nuisance parameters that maximise the likelihood function for a given value of $\mu$. In the absence of any significant deviation from the background expectation, $q_\mu$ is used in the CL$_\text{s}$ method~\cite{Junk:1999kv,Read:2002hq} to set an upper limit on the signal production cross-section times branching ratio at the 95\% CL. For a given signal scenario, values of the production cross-section (parameterised by $\mu$) yielding CL$_\text{s} < 0.05$, where CL$_\text{s}$ is computed using the asymptotic approximation~\cite{Cowan:2010js}, are excluded at 95\% CL. For a $5\sigma$ discovery, the quantity 1-CL$_\text{b}$ must be smaller than $2.87 \cdot 10^{-7}$~\cite{Junk:1999kv} and is also computed using the asymptotic approximation.

@@

Events are required to contain two isolated opposite sign leptons with $\pt > 1$\,TeV, $|\eta|$<4 and an invariant mass \mll\ > 2.5\,TeV.
Figure~\ref{figure:leptonicresonances:ll} left shows the invariant mass for a 30\,TeV \ZpSSM\ signal for the $\mu\mu$ channel. The di-electron invariant mass spectrum is not shown, but as expected from the calorimeter constant term that dominates the resolution at high \pt, the mass resolution is better for the $ee$ channel.
The di-lepton invariant mass spectrum is used as the discriminant and a 50\% normalisation uncertainty on the background normalisation is assumed.
Figure~\ref{figure:leptonicresonances:ll} (bottom left) shows the 95\% CL exclusion limit obtained with 30\,ab$^{-1}$ of data combining ee and $\mu\mu$ channels. Figure~\ref{figure:leptonicresonances:ll} (bottom right) shows the integrated luminosity required to reach a $5\sigma$ discovery as a function of the mass of the heavy resonance. The \Zpee\ and \Zpmumu\ channel display very similar performance due to the low background rates. We conclude therefore that the reference detector design features near to optimal performance for searches involving high \pt\ muon final states. Combining $ee$ and $\mu\mu$ channels, masses up to 42\,TeV can be excluded or discovered. Event yields and limits for $ee$ and $\mu\mu$ alone can be found in Appendix~\ref{app:anamore} and Appendix~\ref{app:yields} respectively.

\begin{figure}[!htb]
  \centering
%  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_ee.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/mzp_sel0_nostack_log_mm.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_ll_fcc_v02_allxs.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ll_comb_rootStyle.eps}
  \caption{Left: Invariant mass for a 30\,TeV signal after full event selection for the $\mu\mu$ channel. Middle: 95\% CL limit versus mass for the combined di-lepton ($ee$, $\mu\mu$) channel. Right: integrated luminosity versus mass for a $5\sigma$ discovery comparing ee, $\mu\mu$ and combined channels.}
  \label{figure:leptonicresonances:ll}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The \texorpdfstring{\tautau}{tautau} final state}
\label{sec:leptautau}
